On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme

### 2020-05-28 LME-MPM.tex
Highlights

%% Group authors per affiliation:
\author{
Miguel Molinos$^a\footnote{Corresponding author: m.molinoss@outlook.es}$
Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es},
Manuel Pastor$^a$
and Miguel Martín Stickle$^a$ 
}
\address{
  $^a$ ETSI Caminos, Canales y Puertos, Universidad Polit\'ectnica de Madrid.\\ c. Prof. Aranguren 3, 28040 Madrid, Spain
}

\begin{abstract}
  \acrfull{mpm} has arisen in the recent years as an
  alternative to \acrfull{fem} under the large
  deformation regime. However, the simulation of shock waves
  propagation and \MP{in the large deformation regime} is still challenging
  under this approach due the incapability of the standard \acrshort{mpm} time
  integration scheme to filter spurious noises. \MP{To overcome it ,
    we propose in this paper an explicit Predictor-Corrector time integration scheme}. Its \textcolor{red}{powerful}
  performance mitigates the presence of spurious oscillations with
  minimal dissipation in high frequency problems. Other source of
  numerical noise in \acrshort{mpm} occurs when the material points
  cross computational grid boundaries, being \MP{caused} by
  the lack of smoothness of the interpolation functions. This noise
  results in spurious local variations at the material points, where
  strain-stress fields are computed. This could lead to inaccurate
  solutions as well as aborted simulations in the worst cases. To
  overcome it, \MP{we propose in this work} the \acrfull{lme} approximation
  schemes as a robust substitute of the traditional shape function in
  \acrshort{mpm}. \acrshort{lme} approximation may be regarded as a
  \textit{thermalization} of Delaunay triangulation which resolves the
  degenerate cases resulting from the lack or uniqueness of the
  triangulation. Furthermore, by modifying a regularization parameter
  they are able to behave finite element like or as a meshfree
  method. This capability allows to face a wide range of physics
  with a single shape function family. Finally this paper demonstrates
  the performance of both improvements thorough numerical examples.    
\end{abstract}

@@

>>>>

%% Group authors per affiliation:
\author{
Miguel Molinos$^a$
Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es},
Manuel Pastor$^a$
and Miguel Mart\'in Stickle$^a$ 
}
\address{
  $^a$ ETSI Caminos, Canales y Puertos, Universidad Polit\'ectnica de Madrid.\\ c. Prof. Aranguren 3, 28040 Madrid, Spain
}

\begin{abstract}
  \acrfull{mpm} has arisen in the recent years as an
  alternative to \acrfull{fem} under the large
  deformation regime. However, the simulation of shock waves
  propagation and \MP{in the large deformation regime} is still challenging
  under this approach due the incapability of the standard \acrshort{mpm} time
  integration scheme to filter spurious noises. \MP{To overcome it ,
    we propose in this paper an explicit Predictor-Corrector time
    integration scheme}. Its \PNA{powerful} performance mitigates the
  presence of spurious oscillations with minimal dissipation in high
  frequency problems. Other source of numerical noise in
  \acrshort{mpm} occurs when the material points cross computational grid boundaries, being \MP{caused} by
  the lack of smoothness of the interpolation functions. This noise
  results in spurious local variations at the material points, where
  strain-stress fields are computed. This could lead to inaccurate
  solutions as well as aborted simulations in the worst cases. To
  overcome it, \MP{we propose in this work} the \acrfull{lme} approximation
  schemes as a robust substitute of the traditional shape function in
  \acrshort{mpm}. \acrshort{lme} approximation may be regarded as a
  \textit{thermalization} of Delaunay triangulation which resolves the
  degenerate cases resulting from the lack or uniqueness of the
  triangulation. Furthermore, by modifying a regularization parameter
  they are able to behave finite element like or as a meshfree
  method. This capability allows to face a wide range of physics
  with a single shape function family. Finally this paper demonstrates
  the performance of both improvements thorough numerical examples.    
\end{abstract}

@@

\begin{highlights}
\item We have proposed a new and efficient time integration scheme for
  the \acrshort{mpm}.
\item The proposal of the \acrshort{lme} approximation technique
  under the \acrshort{mpm} framework as a robust substitute of the
  traditional shape function.
\item Our approach have clear benefits for fast dynamics simulation
  since reduces the presence of spurious oscillations without
  damp the solution. 
\end{highlights}
